%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------

\usepackage{url}
\usepackage{parskip} 	
\usepackage{color}
\usepackage{graphicx}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{mathptmx}

% Setup hyperref package, and colours for links
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{
    colorlinks=true,
    breaklinks=true,
    urlcolor=linkcolour,
    linkcolor=linkcolour,
    pdftitle={Zoey Anastasiadis Resume},
    pdfauthor={Zoey Anastasiadis},
    pdfsubject={Resume}
}

% Custom \section
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{12pt}

% Define centered column type for tabularx
\newcolumntype{C}{>{\centering\arraybackslash}X}

% Tag (framed word or phrase)
\colorlet{body}{black!80!white}
\newcommand{\tag}[1]{%
  \tikz[baseline]\node[anchor=base,draw=body!30,rounded corners,inner xsep=1ex,inner ysep =0.75ex,text height=1.5ex,text depth=.25ex]{#1};
}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% Non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Zoey Anastasiadis} \\[7.0pt]
\href{mailto:zcanast@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ zcanast@gmail.com} \ $|$ \ 
\href{tel:+4432559921}{\raisebox{-0.05\height}\faMobile \ 443.255.9921} \ $|$ \ 
\href{https://github.com/zcanast}{\raisebox{-0.05\height}\faGithub\ zcanast} \ $|$ \ 
\href{https://linkedin.com/in/zoey-anastasiadis}{\raisebox{-0.05\height}\faLinkedin\ zoey-anastasiadis} \\ 
% $|$ \ 
% \href{https://zcanast.github.io/portfolio}{\raisebox{-0.05\height}\faGlobe \ zcanast.github.io/portfolio} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

% Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Stanley Leadership Program - Information Technology} &  \hfill July 2023 - Present \\ 
Stanley Black \& Decker | Remote \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep, leftmargin=1em, itemsep=1pt, label=\textendash]
        \item 2-year rotational program with 4 IT rotations focusing on leadership and technical expertise.
        \item Co-lead of Sustainable Development Committee, organizing newsletters, speaker series, and volunteering events.
    \end{itemize}
    \end{minipage}
}\

\hspace{1em}\textbf{4th Rotation: GenAI App Architecture} &  \hfill January 2025 - Present \\  
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep, leftmargin=2em, itemsep=3pt, label=\textendash]
        \item Designed and implemented an AI chatbot using Zenlytic, enhancing data exploration and reducing retrieval times.
        \item Integrated real-time data into Zenlytic for streamlined business analysis processes.
        \item Built and maintained semantic models, ensuring accessible and up-to-date data organization.
        \item Conducted user feedback sessions to improve AI features and user satisfaction.
        \item Tested and refined AI functionalities, ensuring robust performance and adoption.
    \end{itemize}
    \end{minipage}
}\

\hspace{1em}\textbf{3rd Rotation: Data Architect} &  \hfill July 2024 - January 2025 \\ 
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep, leftmargin=2em, itemsep=3pt, label=\textendash]
        \item Automated KPI calculations using Snowflake SQL and Python, saving ~40 hours/month.
        \item Developed Power BI dashboards for leadership, visualizing usage trends and improving decision-making.
        \item Implemented AWS Lambda functions to optimize processes, saving \$20,000 annually.
        \item Created vendor support documentation for efficient ticketing processes.
        \item Evaluated AWS WorkSpaces, identifying inefficiencies and reducing costs by $20,000/year.
    \end{itemize}
    \end{minipage}
}\

\hspace{1em}\textbf{2nd Rotation: Architecture Process Engineer} &  \hfill January 2024 - July 2024 \\ 
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep, leftmargin=2em, itemsep=3pt, label=\textendash]
        \item Enhanced data quality in Ardoq, improving certification scores by 33\%.
        \item Automated metadata extraction for 40,000 product manuals, saving 650 productivity hours.
        \item Designed dashboards in Power BI to track survey progress and certification metrics.
        \item Developed a Python script to generate app descriptions, raising completion scores by 33\%.
        \item Organized training demos and created tools for capability team data certification.
    \end{itemize}
    \end{minipage}
}\

\hspace{1em}\textbf{1st Rotation: Process Analyst} &  \hfill July 2023 - January 2024 \\ 
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep, leftmargin=2em, itemsep=3pt, label=\textendash]
        \item Conducted data analysis to identify trends in project changes, improving process efficiency.
        \item Proposed a repeatable process for lessons-learned data analysis, enabling biannual reporting.
        \item Created data-driven presentations to support decision-making and foster evidence-based discussions.
        \item Identified key project change reasons using Excel, enabling proactive risk mitigation.
        \item Delivered insights through Power BI and Miro, advancing project management strategies.
    \end{itemize}
    \end{minipage}
}\

\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{iSchool Undergraduate Assistant for Research Programs} &  \hfill January 2022 - May 2023 \\ 
University of Maryland, College of Information Studies | College Park, MD \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Facilitated research communications and data analysis for the Associate Dean of Research.
        \item Prepared Excel reports to support decision-making and improve research workflows.
        \item Updated WordPress websites, ensuring high-quality online resources through QA checks.
        \item Configured video conferencing for research events and presentations.
        \item Collaborated on research-related projects, improving workflows and event execution.
    \end{itemize}
    \end{minipage}
}\

\textbf{Technology Intern} &  \hfill June 2022 - August 2022 \\ 
Stanley Black \& Decker | Remote \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Managed training sessions for 450+ IT employees, tracking attendance with Excel.
        \item Created explainer videos using Powtoon to improve onboarding and training processes.
        \item Designed and analyzed Mentimeter questionnaires to enhance training effectiveness.
        \item Maintained SharePoint sites to disseminate communications across the organization.
        \item Presented training data in visually compelling formats to improve engagement.
    \end{itemize}
    \end{minipage}
}\

\end{tabularx}

%----------------------------------------------------------------------------------------
% PROJECTS SECTIONS
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Crime in Prince George's County, MD} & \hfill \href{https://zcanast.github.io/crime-trends/}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Built an interactive web page using HTML, CSS, and JavaScript to analyze crime trends.
        \item Integrated API data and visualized incidents with Chart.js and Leaflet libraries.
        \item Enabled users to explore crime statistics interactively through a user-friendly interface.
        \item Improved public awareness by making data accessible and visually engaging.
        \item Demonstrated proficiency in web development and data visualization tools.
    \end{itemize}
    \end{minipage}
}\

\end{tabularx}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
\textbf{University of Maryland} | College Park, MD &  \hfill \normalsize May 2023 \\ 
Bachelor of Science in Information Science & \hfill \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}

\textbf{Languages} & \normalsize
\tag{Python}
\tag{Java}
\tag{SQL}
\tag{HTML/CSS}
\tag{JavaScript}
\\

\textbf{Technologies}  &  \normalsize{
\tag{Excel}
\tag{AWS}
\tag{Power BI}
\tag{Tableau}
\tag{Snowflake}
}\\

\end{tabularx}

\vfill
% \center{\footnotesize Last updated: \today}

\end{document}
